\section{Shout / Isley Brothers}\label{sec:shout}

\Fmajor
\Dminor
\BflatSeven


\textbf{Intro}

We-eee-eeel....      \\                       
You know you make me wanna \upchord{F}(Shout!) Kick my heels up and \upchord{Dm}(Shout!)\\
Throw my hands up and \upchord{F}(Shout!) Throw my head back and \upchord{Dm}(Shout!)\\
Come on now \upchord{F}(Shout!) Don't forget to say you \upchord{Dm}will\\
\upchord{F}Don't forget to say, yeah \upchord{Dm}Yeah, yeah, yeah, yeah\\
\upchord{F}(Say you \upchord{Dm}will) Say it right now bab-ay\\
\upchord{F}(Say you \upchord{Dm}will) Come on, come on\\
\upchord{F}(Say you \upchord{Dm}will) Say it, will-a you-ooooo!\\
\upchord{F}(Say you \upchord{Dm}will) Come on Now\\
\upchord{F}(Say) say that you love me \upchord{Dm}(Say) say that you need me\\
\upchord{F}(Say) say that you want me
\upchord{Dm}(Say) you wanna please me \upchord{F}(Say) come on now \\
\upchord{Dm}(Say) come on now  \upchord{F}(Say) come on now  \upchord{Dm}(Say)...\\
I still re\upchord{F}member (Shooby-doo-wop-do-wop-wop-wop-wop)\\
When you used to be nine years \upchord{Dm}old (Shooby-doo-wop-do-wop-wop-wop-wop) Yeah-yeah!\\
I was a \upchord{F}fool for you, from the bottom of my \upchord{Dm}soul, yeah!\\
(Shooby-doo-wop-do-wop-wop-wop-wop) Now that you've \upchord{F}grown, up\\
(Shooby-doo-wop-do-wop-wop-wop-wop) Up enough to \upchord{Dm}know, yeah yeah\\
(Shooby-doo-wop-do-wop-wop-wop-wop) You wanna \upchord{F}leave me, you wanna, let me \upchord{Dm}go\\
(Shooby-doo-wop-do-wop) I want you to \upchord{F}know\upchord{Bb7}    \upchord{F}\\
I said I \upchord{F}want you to \upchord{Bb7}know \upchord{F}right now, yeah!\upchord{Bb7}        \upchord{F}\\
You been \upchord{Bb7}good to me \upchord{F}baby\upchord{Bb7}\\
\upchord{F}Better than I \upchord{Bb7}been to my\upchord{F}self, hey! hey!\upchord{Bb7}       \upchord{F}\\
And if you \upchord{Bb7}ever leave me\upchord{F} \upchord{Bb7}      \upchord{F}\\
I don't \upchord{Bb7}want nobody \upchord{F}else, hey! hey!\upchord{Bb7}         \upchord{F}\\
I said I \upchord{Bb7}want you to \upchord{F}know-ho-ho-hey!\upchord{Bb7}         \upchord{F}\\
I said I \upchord{Bb7}want you to \upchord{F}know right now, hey! hey!\upchord{Bb7}         \upchord{F}          \upchord{Bb7}\\
You know you \upchord{Bb7}make me wanna \upchord{F}(Shout-wooo) hey-yeah\\
\upchord{Dm}(Shout-wooo) yeah-yeah-yeah \upchord{F}(Shout-wooo) aaaalll-right\\
\upchord{Dm}(Shout-wooo) aaaalll-right\\
\upchord{F}(Shout-wooo) come on now! \upchord{Dm}(Shout) come on now!\\
\upchord{F}(Shout) yeah, yeah, yeah \upchord{Dm}(Shout) yeah, yeah, yeah (good sound)\\
\upchord{F}(Shout) yeah, yeah, yeah (good sound)\\
\upchord{Dm}(Shout) yeah, yeah, yeah (good sound)\\
\upchord{F}(Shout) all-alright (good sound)\\
\upchord{Dm}(Shout) it's all-alright (good sound)\\
\upchord{F}(Shout) all-alright (good sound)\\
\upchord{Dm}(Shout) all-alright (aah) \upchord{F} -STOP- (Shout)\\
Now wai-a-ait A \upchord{F}minute!\\
I feel aaaaaaallllllright! (Yeah-Yeah, Yeah-Yeah, Yeah-Yeah) (OOOOOOOOW)\\	
Now that I got my woman I feel aaaaaaaalllll\upchord{Bb7}right!\\
(Yeah-Yeah, Yeah-Yeah, Yeah-Yeah)\\
Every time I think about you You been so good to me\\
You know you make me wanna\ \upchord{F}(Shout-wooo) lift my heels up and\\
\upchord{Dm}(Shout-wooo) throw my head back and\\
\upchord{F}(Shout-wooo) kick my heels up and\\
\upchord{Dm}(Shout-wooo) come on now \upchord{F}(Shout-wooo) take it easy\\
\upchord{Dm}(Shout-wooo) take it easy \upchord{F}(Shout-wooo) take it easy (higher)\\
\upchord{Dm}(Shout) a little bit softer now (?x)\\
\upchord{F}(Shout) a little bit louder now (?x) (Shout)\\
Hey-HeyA Hey (Hey-HeyA Hey)\\ HeyA HeyA  (HeyA HeyA) (x2) \\
JUMP NOW! Jump up and shout now (wooo)\\
Jump up and shout now (wooo) (x4)\\ 
Everybody shout now Everybody shout now\\
Everybody, shout, shout\\
Shout, shout, shout (x ad lib)\\
Everybody shout now (ooo)\\
