\section{Shut Up and Dance With Me / Walk the Moon}\label{sec:shutupanddancewithme}

\Gmajor
\Cmajor
\Fmajor
\Aminor

\textbf{Chorus}

\upchord{G} "Oh don't you \upchord{C} dare look \upchord{F} back.

Just keep your \upchord{Am} eyes on \upchord{G} me."

I said, "You're \upchord{C} holding \upchord{F} back, "

She said, "Shut \upchord{Am} up and \upchord{G} dance with \upchord{C} me!"

This \upchord{F} woman is my \upchord{Am} destiny \upchord{G}

She said, "\upchord{C} Ooh-ooh-\upchord{F} hoo, shut \upchord{Am} up and \upchord{G} dance with \upchord{C} me."

\textbf{Verse 1}

\upchord{F} \upchord{G} \upchord{Am} \upchord{G}  X 2

We were \upchord{C} victims \upchord{F} of the \upchord{Am} night,

The \upchord{G} chemical, \upchord{C} physical, \upchord{F} kryptonite \upchord{Am}

\upchord{G} Helpless to the \upchord{C} bass and the \upchord{F} fading \upchord{Am} light

\upchord{G} Oh, we were \upchord{C} bound to get to\upchord{F}gether, \upchord{Am} bound to get to\upchord{G}gether.


She \upchord{C} took my \upchord{F} arm, I don't know \upchord{Am} how it \upchord{G} happened.

We \upchord{C} took the \upchord{F} floor and she \upchord{G} said,

\textbf{Repeat Chorus}

\textbf{Verse 2}

A backless \upchord{C} dress and some \upchord{F} beat up \upchord{Am} sneaks,

My \upchord{G} discothèque, \upchord{C} Juliet \upchord{F} teenage \upchord{Am} dream.

I \upchord{G} felt it in my \upchord{C} chest as she \upchord{F} looked at \upchord{Am} me. \upchord{G}

I knew we were \upchord{C} bound to be to\upchord{F}gether,

\upchord{Am} Bound to be to\upchord{G}gether

She \upchord{C} took my \upchord{F} arm, I don't know \upchord{Am} how it \upchord{G} happened.

We \upchord{C} took the \upchord{F} floor and she \upchord{C} said,

\textbf{Repeat Chorus}

\textbf{Bridge}

\upchord{F} Oh, come on girl! \upchord{F} \upchord{G} \upchord{Am} \upchord{G}  X 4

\upchord{C} Deep in her \upchord{F} eyes, I think I \upchord{Am} see the \upchord{G} future.

I \upchord{C} realize \upchord{F} this is my last \upchord{G} chance.

She \upchord{C} took my \upchord{F} arm, I don't know \upchord{Am} how it \upchord{G} happened.

We \upchord{C} took the \upchord{F} floor and she \upchord{G} said,

\textbf{Repeat Chorus x 2}

