\section{Ho Hey / The Lumineers}\label{sec:hohey}
\emph{The F then C chords - you have to play the F really quickly for half a beat. It's mostly C}
\Fmajor
\Cmajor
\Gmajor
\Aminor
  
\upchord{F}\upchord{C}Ho! \upchord{F}\upchord{C}Hey! \upchord{F}\upchord{C}Ho! \upchord{F}\upchord{C}Hey!\\
\upchord{F}\upchord{C}Ho! I've been trying to do it right \upchord{F}\upchord{C}Hey! I've been living a lonely life\\
\upchord{F}\upchord{C}Ho! I've been sleeping here instead \upchord{F}\upchord{C}Hey! I've been sleeping in my bed\\
\upchord{Am}Ho! Sleeping \upchord{G}in my bed\upchord{C}Hey! \upchord{F}\upchord{C}Ho!\\
\upchord{F}\upchord{C}Ho! So show me family \upchord{F}\upchord{C}Hey! All the blood that I would bleed\\
\upchord{F}\upchord{C}Ho! I don't know where I belong \upchord{F}\upchord{C}Hey! I don't know where I went wrong\\
\upchord{Am}Ho! But I can \upchord{G}write a song\upchord{C}Hey! \emph{One-two-three}\\
I belong with \upchord{Am}you... you belong with \upchord{G}me\\
You're my sweet\upchord{C}heart\\
I belong with \upchord{Am}you... you belong with \upchord{G}me,	\\	
You're my sweet\upchord{C}Ho! \upchord{F}\upchord{C}Hey! \upchord{F}\upchord{C}Ho! \upchord{F}\upchord{C}Hey!\\
\upchord{F}\upchord{C}Ho! I don't think you're right for him\\
\upchord{F}\upchord{C}Hey! Look at what it might have been if you\\
\upchord{F}\upchord{C}Ho! took a bus to China Town\\
\upchord{F}\upchord{C}Hey! I'd be standing on Canal\\
\upchord{Am}Ho! and \upchord{G}Bowery\upchord{C}Hey!\upchord{Am}Ho! And she'd be standing \upchord{G}next to me\\
\upchord{C}Hey! \emph{One-two-three}\\
I belong with \upchord{Am}you... you belong with \upchord{G}me\\
You're my sweet\upchord{C}heart\\
I belong with \upchord{Am}you... you belong with \upchord{G}me\\
You're my sweet\upchord{C}Heart\\
And \upchord{Am}lo-o-ove... we \upchord{G}need... it \upchord{C}now\\
Let's \upchord{Am}ho-o-ope for \upchord{G}some\\
Cause \upchord{Am}o-o-oh... we're \upchord{G}bleeding \upchord{C}out\\
I belong with \upchord{Am}you... you belong with \upchord{G}me\\
You're my sweet\upchord{C}heart\\
I belong with \upchord{Am}you... you belong with \upchord{G}me\\
You're my sweet\upchord{C}Ho! \upchord{F}\upchord{C}Hey! \upchord{F}\upchord{C}Ho! \upchord{F}\upchord{C}He-e-ey!\\
