\section{Damn These Vampires / The Mountain Goats}\label{sec:damnthesevampires}

\Amajor
\Gmajor
\FsharpMinor
\DmajorEasy
\EmajorEasy


\upchord{A}Brave young \upchord{G}cowboys, Of the near north \upchord{F\#m}side

Mount those \upchord{D}bridge rails, Ride all \upchord{A}night

Scream when \upchord{G}captured, Arch your \upchord{F\#m}back

Let this \upchord{A}whole town \upchord{E}hear your \upchord{D}knuckles crack

\upchord{A}Sapphire \upchord{G}Trans-Am. High beams in \upchord{F\#m}vain

Drive wild \upchord{D}broncos, Down the \upchord{A}plain

Push up to the \upchord{G}corner. Where the turbines \upchord{F\#m}hiss

Some \upchord{A}day we \upchord{E}won't rem\upchord{D}ember this

Crawl 'til \upchord{A}dawn. On my hands and \upchord{D}knees

\upchord{D}God damn these \upchord{A}vampires

For \upchord{E}what they've done to me\upchord{D}

\upchord{A}Tie those \upchord{G}horses to the post out\upchord{F\#m}side

And let those \upchord{D}glass doors open wide \upchord{A}

And in their \upchord{G}surface. See two young, savage \upchord{F\#m}things

\upchord{A}Barely \upchord{E}worth re\upchord{D}membering

\upchord{A}Feast like \upchord{G}pagans. Never get e\upchord{F\#m}nough

Sleep like \upchord{D}dead men. Wake up like \upchord{A}dead men

And when the \upchord{G}sun comes. Try not to hate the \upchord{F\#m}light

Some\upchord{A}day we'll \upchord{E}try to \upchord{D}walk upright

Crawl 'til \upchord{A}dawn. On my hands and \upchord{D}knees

\upchord{D}God damn these \upchord{A}bite marks

\upchord{E}Deep in my arteries\upchord{D}

Crawl 'til \upchord{A}dawn
    
On my hands and \upchord{D}knees

\upchord{D}God damn these \upchord{A}vampires

For \upchord{E}what they've done to me\upchord{D}

\upchord{A} \upchord{G} \upchord{F\#m} x3

\upchord{A} \upchord{E} \upchord{D}
