\section{Dancing in the Dark / Bruce Springsteen}\label{sec:dancinginthedark}

\Gmajor
\Eminor
\Cmajor
\Aminor
\DmajorEasy

\textbf{intro} \upchord{G} \upchord{Em} \upchord{G} \upchord{Em}\\
\upchord{G} I get up in the \upchord{Em}evening… \upchord{G} and I \upchord{Em}ain’t got nothing to \upchord{G}say\\
I come home in the \upchord{Em}morning… \upchord{G} I go to bed \upchord{Em}feeling the same \upchord{C}way\\
I ain't nothing but \upchord{Am}tired… \upchord{C} man I'm just \upchord{Am}tired and bored with my\upchord{G}self\\
Hey there \upchord{Em}baby… \upchord{G} I could \upchord{Em}use just a little \upchord{D}help\\
You can't start a \upchord{D}fi-re… you can't start a fire without a \upchord{C}spark\\
This gun's for \upchord{Am}hi-re… \upchord{C} even if we're just \upchord{Am}dancing in the \upchord{G}dark\\
\upchord{Em} \upchord{G} \upchord{Em}\\
\upchord{G} Messages keep getting \upchord{Em}clearer… \upchord{G} radio's on and I'm \upchord{Em}moving 'round the \upchord{G}place\\
I check my look in the \upchord{Em}mirror… \upchord{G} wanna change my \upchord{Em}clothes my hair my \upchord{C}face\\
Man I ain't getting \upchord{Am}nowhere… \upchord{C} I'm just \upchord{Am}living in a dump like \upchord{G}this\\
There's something happening \upchord{Em}somewhere… \upchord{G} baby I \upchord{Em}just know that there \upchord{D}is\\
You can't start a \upchord{D}fi-re… you can't start a fire without a \upchord{C}spark\\
This gun's for \upchord{Am}hi-re… \upchord{C} even if we're just \upchord{Am}dancing in the \upchord{G}dark\\
\upchord{Em} \upchord{G} \upchord{Em}\\
\upchord{Em} You sit around getting \upchord{G}older… \upchord{C} there's a joke here some\upchord{D}where and it's on \upchord{Em}me\\
I'll shake this world off my \upchord{G}shoulders… \upchord{C} come on baby the \upchord{D}laugh's on me\\
\upchord{G} Stay on the streets of \upchord{Em}this town… \upchord{G} and they'll be \upchord{Em}carving you up all \upchord{G}right\\
They say you gotta stay \upchord{Em}hungry… \upchord{G} hey baby, I'm \upchord{Em}just about starving to\upchord{C}night\\
I'm dying for some \upchord{Am}action… \upchord{C} I'm sick of sitting \upchord{Am}round here trying to write this \upchord{G}book\\
I need a love re\upchord{Em}action… \upchord{G} come on \upchord{Em}baby give me just one \upchord{D}look\\
You can't start a \upchord{D}fi-re… sitting round crying over a broken \upchord{C}heart\\
This gun's for \upchord{Am}hire… \upchord{C} even if we're just \upchord{Am}dancing in the \upchord{G}dark\\
You can't start a \upchord{D}fi-re… worrying about your little world falling a\upchord{C}part\\
This gun's for \upchord{Am}hire… \upchord{C} even if we're just \upchord{Am}dancing in the \upchord{G} dark\\
\textbf{outro – repeat to fade} \upchord{G} \upchord{Em} \upchord{G} \upchord{Em}
