\section{Hounds of Love / Kate Bush}\label{sec:hounds_of_love}
  {\small We need different people doing the doos, ows, and in-the-trees from those singing the bridge parts. The rhythm in this is a bit of a fucker. We'll probably need someone banging a drum.}
  
  \Fmajor
  \Cmajor
  \BflatMajor
  \Aminor
  \DminorSeven
  
  It's in the trees!
  It's coming!\\
  Chorus:\\
  \upchord{F}When I was a \upchord{C}child:
  running in the \upchord{Bb}night,\\
  Af\upchord{Bb}raid of what might \upchord{F}be -
  hiding in the \upchord{C}dark,\\
  Hiding in the \upchord{Bb}street,
  And of \upchord{Bb}what was following \upchord{Dm}me...\\
  Verse:\\
  doo doo \upchord{C}doo doo doo\upchord{Bb}
  now hounds of \upchord{Am}love are haunting \upchord{Dm}me. \\
  oo oo\upchord{Bb} oo oo oo \upchord{Am}
  I've always \upchord{C}been a coward\upchord{Dm},\\
  oo oo\upchord{Bb} oo oo oo \upchord{Am}
  and I don't \upchord{C}know what's good for me.\upchord{Dm}\\
  Bridge:\\
  \upchord{Dm}
  Here I \upchord{F}go!
  \upchord{Dm7}It's coming \upchord{Bb}for me through the \upchord{Bb}trees.\upchord{F}\\
  Help me, \upchord{Dm7}someone!
  help me, \upchord{Bb}please!\upchord{Bb}\\
  \upchord{F}Take my \upchord{Dm7}shoes off,
  and \upchord{Bb}throw them in the lake\upchord{Bb},\\
  And I'll \upchord{F}be
  \upchord{Dm7}two steps on the \upchord{Bb}water.\upchord{Bb}\\
  \upchord{F}I found a \upchord{C}fox
  caught by \upchord{Bb}dogs.\\
  He let me \upchord{Bb}take him in my \upchord{F}hands.
  his little \upchord{C}heart,\\
  It beat so \upchord{Bb}fast,
  and I'm \upchord{Bb}ashamed of running \upchord{F}away\\
  From nothing \upchord{C}real--
  I just can't \upchord{Bb}deal with this,\\
  But \upchord{Bb}I'm still afraid to \upchord{Dm}be there,
  doo doo\upchord{C} doo doo doo doo\upchord{Bb}\\
  Among your \upchord{Am}hounds of love,\upchord{Dm}
  ow ow\upchord{Bb} ow ow ow ow\upchord{Am}\\
  And feel your \upchord{C}arms surrounding \upchord{Dm}me.
  ow ow \upchord{Bb}ow ow ow ow\upchord{Am}\\
  I've always \upchord{C}been a coward\upchord{Dm},\\
  \upchord{Bb}And never \upchord{Am}know what's good for \upchord{C}me.\upchord{Dm}\\
  \\
  \upchord{Dm}
  Oh, here I \upchord{F}go!
  \upchord{F}Don't let me \upchord{Bb}go!\\
  \upchord{Bb}Hold me \upchord{F}down!
  It's \upchord{F}coming for me \upchord{Bb}through the trees.\upchord{Bb}\\
  \upchord{F}Help me, \upchord{F}darling,
  Help me, \upchord{Bb}please!\upchord{Bb}\\
  \upchord{F}Take my \upchord{F}shoes off
  and \upchord{Bb}throw them in the \upchord{Bb}lake,\\
  And I'll be\upchord{F}\\
  \upchord{F}Two steps on the \upchord{Bb}water. \upchord{Bb}\\
  \upchord{F}I don't know what's \upchord{F}good for me.\\
  I don't know what's \upchord{Bb}good for me.\\
  I need your \upchord{Bb}la la la la la la, \upchord{F}yeahie yo \upchord{F}yeahie yo !
  \upchord{Bb}Your love!\\
  do do do\upchord{Bb}
  \upchord{F}Take your \upchord{F}shoes off\\
  And \upchord{Bb}throw them in the \upchord{Bb}lake!
  \upchord{F}Do you know what I \upchord{F}really need?\\
  Do you know what I \upchord{Bb}really need?\\
  I need \upchord{Bb}love love love love love, \upchord{F}yeah!\\
