\section{Carol Brown / Flight of the Conchords}\label{sec:carolbrown}

\DmajorEasy
\Amajor
\FsharpMinor
\Bminor
\Eminor

RIFF:\\
\texttt{-5-2-4542-420}\\
\texttt{-------------}\\
\texttt{2------------}\\
\texttt{-------------}\\

\upchord{D}Loretta.\upchord{A}Broke my heart in a letter\\
She told me she was leaving and her life would be better\\
Joan. Broke it off over the phone \upchord{D} After the ton, she left me alone\\
Jen said she'd never ever see me again\upchord{A}When I saw her again she said it again\\
Jan. Met another man \upchord{D}Leeza got amnesia. Just forgot who I am\\
Felicity Said there was no electricity\\
\upchord{A}Emily. No chemistry. Fran, ran. Bruce turned out to be a man\\
\upchord{D}Flo had to go I couldn't go with the flow\\
CHORUS\\
\upchord{F\#m}Carol Brown. Just took a \upchord{Bm}bus out of town\\
But I'm hoping that you'll stick around (RIFF)\\
BRIDGE\\
\upchord{Em}He doesn't cook or clean he's not \upchord{D}good boyfriend mat\upchord{A}erial.\\
 (Oh, we can eat cereal)\\
\upchord{Em}You'll lose interest fast . His re\upchord{D}lationships never last\upchord{A}\\
 (Shut up, girlfriends from the past)\\
\upchord{Em}He says he'll do one thing and then he\\
 \upchord{D}goes and does an\upchord{A}other thing\\
\upchord{Em}(Ohh, who organized all of my ex-girlfriends into a \upchord{D}choir\\
and got them to \upchord{A}sing?)\\
\upchord{Em}Ah, ah, ah, \upchord{D}ahh, ah, ah, \upchord{A}ah (Who, who? Hmm, shut up)\\
\upchord{Em}Ah, ah, ah, \upchord{D}ahh, ah, ah, \upchord{A}ah \upchord{D}\\
(Shut up, girlfriends from the past)\\
\upchord{D} x 4\\
\upchord{D}Mimi Will no longer see me. \upchord{A} Britney. Britney hit me\\
\upchord{D}Paula, Persephone, Stella and Stephanie.\\
\upchord{D}There must be fifty ways that lovers have left me\\
CHORUS\\
\upchord{F\#m}Carol Brown. Just took a \upchord{Bm}bus out of town\\
\upchord{Em}Love is a delicate thing. It could just float away on the \upchord{D}breeze    \upchord{A}.\\
 (He said the same thing to me)\\
\upchord{Em}How can we ever know we've found the right person in this world?\\
\upchord{D} \upchord{A}\\
(He means he looks at other girls)\\
\upchord{Em}Love is a mystery it does not follow a \upchord{D}rule  \upchord{A}\\
(This guy is a fool)\\
\upchord{Em}(He'll always be a boy. He's a man who never grew \upchord{D}up)  \upchord{A}	\\
I thought I told you to shut-uh-uh-up\\
\upchord{Em}(Ah, ah, ah, \upchord{D}ahh) Mona, you told me you were in a coma\\
 (ah, ah, \upchord{A}ah)\\
\upchord{Em}(Ah, ah, ah, \upchord{D}ahh) Tiffany, you said that you had an epiphany\\
 (ah, ah, \upchord{A}ah)\\
\upchord{Em}(Ah, ah, ah, \upchord{D}ahh) Mmm, would you like a little cereal?\\
(ah, ah, \upchord{A}ah)\\
\upchord{Em}(Ah, ah, ah, \upchord{D}ahh)who organized this choir of ex-girlfriends?\\
(ah, ah, \upchord{A}ah) \\
Was it you, Carol Brown? Was it you, Carol Brown?\\
\upchord{F\#m}Carol Brown. Just took a \upchord{Bm}bus out of town\\
But I'm hoping that you'll \upchord{D}stick around (RIFF)\\
\upchord{D}Stick around (RIFF)(doo, doo, doo, doo, doo, doo, doo, doo)\\
Stick around (RIFF)(doo, doo, doo, doo, doo, doo)\\
(RIFF)Doo, doo, doo, doo, doo, doo\\
Stick around\\
(RIFF)Doo, doo, doo, doo, doo, doo\\
Stick around
