\section{Christmas Wrapping / The Waitresses}\label{sec:christmas_wrapping}
{\small (Half the group play F\#m7-Em7-Dm7-C\#m7 progression through the verse.)}

\Amajor
\Bmajor
\CmajorFirst
\DmajorFirst
\Eminor
\Gmajor

\Afive
\Bfive
\CsharpFive

\FsharpMinorSevenNoFive
\EMinorSevenNoFive
\DMinorSevenNoFive
\CsharpMinorSevenNoFive


Intro x2 

\upchord{A} ---- \upchord{A} ---- \upchord{D} ---- \upchord{C} -- \upchord{B}\\

\upchord{A}Bah Humbug; now that's too strong!

'Cause it is my favorite holiday.

But \upchord{D}all this year's been a busy blur

Don't \upchord{C}think I have the \upchord{B}energy

To \upchord{A}add to my already mad rush

Just 'cause it's 'tis the season.

The \upchord{D}perfect gift for me would be

Com-\upchord{C}pletions and con-\upchord{B}nections left from 

\upchord{A}last year. Ski shop, Encounter most interesting.

\upchord{D}Had his number but never the time,

\upchord{C}Most of `81 passed a-\upchord{B}long those lines.

So \upchord{A}deck those halls. Trim those trees.

Raise up cups of Christmas cheer.

\upchord{D}I just need to catch my breath,

\upchord{B5}Christmas by \upchord{A5}my-\upchord{C$\sharp$5}self \upchord{A5}this \upchord{A5}year\upchord{A5} \upchord{A5} \upchord{A5}

\upchord{A}Calendar picture. Frozen landscape,

Chill this room for twenty-four days.

\upchord{D}Evergreens. Sparkling snow.

\upchord{C}Get this winter over with!

\upchord{B}....Flashback to \upchord{A}springtime, saw him again,

Would have been good to go for lunch.

\upchord{D}Couldn't agree when we were both free.

We \upchord{C}tried, we said we'd \upchord{B}keep in touch.

\upchord{A}Didn't of course `till summer time,

Out to the beach to his boat could I join him?

\upchord{D}No, this time it was me;

\upchord{C}Sunburn in the \upchord{B}third degree.

\upchord{A}Now the calendar's just one page

Of course I am excited.

To-\upchord{D}night's the night I've set my mind

Not to \upchord{B5}do too much \upchord{A5}a-\upchord{C$\sharp$5}bout \upchord{A5}it.\upchord{A5} \upchord{A5} \upchord{A5}

Interlude 1 \upchord{D} ---- \upchord{G} ---- \upchord{D} ---- \upchord{G} -- \upchord{D} x3

\upchord{D} ---- \upchord{G} ---- \upchord{D} ---- ---- \upchord{G} -- \upchord{D} ---- \upchord{Eminor} -- \upchord{D} 


\upchord{A5}Merry Christmas; Merry Christmas

But I think I'll miss this one this year.

Merry Christmas; Merry Christmas

But I think I'll miss this one this year.

Merry Christmas; Merry Christmas

But I think I'll miss this one this year.

Merry Christmas; Merry Christmas

But I think I'll miss this one this year.

\upchord{A}Hardly dashing through the snow

`Cause I bundled up too tight.

\upchord{D}Last minute have-to-dos:

A few \upchord{C}cards, a few \upchord{B}calls

`Cause it's \upchord{A}R-S-V-P,

No thanks, no party lights.

It's \upchord{D}Christmas Eve, gonna relax,

\upchord{C}Turned down all of \upchord{B}my invites.

\upchord{A}Last fall I had a night to myself

Same guy called, Halloween party.

\upchord{D}Waited all night for him to show,

\upchord{C}This time his car \upchord{B}wouldn't go.

For-\upchord{A}get it, it's cold, it's getting late.

Trudge on home to celebrate.

In a \upchord{D}quiet way, unwind,

\upchord{B5}Doing Christ-\upchord{A5}mas \upchord{C$\sharp$}right \upchord{A5}this \upchord{A5}time. \upchord{A5} \upchord{A5} \upchord{A5}

\upchord{A}A\&P has provided me

With the world's smallest turkey.

Al-\upchord{D}ready in the oven, nice and hot.

Oh \upchord{C}damn! Guess what \upchord{B}I forgot.

So \upchord{A}on with the boots, back out in the snow

To the only all-night grocery.

When \upchord{D}what to my wondering eyes should appear,

In the \upchord{C}line is that guy I've been \upchord{B}chasing all year!

``I'm \upchord{A}spending this one alone," he said.

``Need a break; this year's been crazy."

I \upchord{D}said ``Me too, but why are you?

You \upchord{C}mean you forgot cran-\upchord{B}berries too?"

Then \upchord{A}suddenly we laughed and laughed,

Caught on to what was happening.

That \upchord{D}Christmas magic's brought this tale,

To a \upchord{B5}very hap-\upchord{A5}py \upchord{C$\sharp$}end-\upchord{A5}ing. \upchord{A5} \upchord{A5} \upchord{A5}

\upchord{A5}Merry Christmas! Merry Christmas!

Couldn't miss this one this year!

Repeat to fade






