\section{Country Roads / John Denver}\label{sec:countryroads}

\Aminor
\BflatMajor
\Cmajor
\Fmajor
\Gmajor
\Gseven

\upchord{C} Almost heaven… \upchord{Am} West Virginia\\
\upchord{G} Blue ridge mountains \upchord{F} Shenandoah \upchord{C} river\\
\upchord{C} Almost heaven… \upchord{Am} West Virginia\\
\upchord{G} Blue ridge mountains \upchord{F} Shenandoah \upchord{C} river\\
\upchord{C} Life is old there \upchord{Am} older than the trees\\
\upchord{G} Younger than the moun-tains… \upchord{F} blowing like a \upchord{C} breeze\\

Country \upchord{C} roads… take me \upchord{G} home\\
To the \upchord{Am} place… I be\upchord{F}long\\
West Vir\upchord{C}ginia… mountain \upchord{G} mama\\
Take me \upchord{F}home… country \upchord{C} roads\\

\upchord{C} All my memories… \upchord{Am} gathered round her\\
\upchord{G} Miner’s lady… \upchord{F} stranger to blue \upchord{C} water\\
\upchord{C} Dark and dusty… \upchord{Am} painted on the sky\\
\upchord{G} Misty taste of moonshine \upchord{F} teardrops in my \upchord{C} eye\\

Country \upchord{C} roads… take me \upchord{G7} home\\
To the \upchord{Am} place… I be-\upchord{F} long\\
West Vir-\upchord{C}ginia… mountain \upchord{G} mama\\
Take me \upchord{F} home… country \upchord{C} roads\\

\upchord{Am} I hear her \upchord{G} voice in the \upchord{C}  mornin’ hour she calls me\\
The \upchord{F} radio re-\upchord{C}minds me of my \upchord{G} home far away\\
And \upchord{Am} drivin’ down the \upchord{Bb} road I get a feel-\upchord{F}in’ that I\\
\upchord{C} should have been home \upchord{G} yesterday… yester-\upchord{G7}day\\

Country \upchord{C} roads… take me \upchord{G} home\\
To the \upchord{Am} place… I be\upchord{F} long\\
West Vir-\upchord{C}ginia… mountain \upchord{G} mama\\
Take me \upchord{F} home… country \upchord{C} roads\\
Take me \upchord{G} home… down country \upchord{C} roads\\
Take me \upchord{G} home… down country \upchord{C} roads \upchord{C} (single strum)\\






